Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-15 paper/paper.tex
reduced number of graphs & added extra columns to autotable

\newcommand{\hgt}{2.9cm}
\newcommand{\LGCLine}{blue}
\newcommand{\RGCLine}{red}
\newcommand{\ReachLine}{black}
\newcommand{\UseLine}{light-blue}

\begin{figure*}[t!]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}@{}c@{}@{}c@{}}
   \hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nperm.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=paraffins.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=lcss.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=huffman.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=knightstour.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=deriv.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=treejoin.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=lambda.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=gc_bench.eps, height=\hgt}}
%\\ (a) & (b)
\end{tabular}
\vspace*{-2mm}
 \caption{Memory usage.  
The \RGCLine\ and the \LGCLine\ curves indicate the number of cons
cells  in  the  active   semi-space  for  RGC  and  LGC
respectively.  The \ReachLine\ curve represents the number of
reachable cells and the  \UseLine\ curve represents the
number  of  cells  that  are actually  live  (of  which
liveness analysis does a static approximation).  x-axis
is the time measured  in number of cons-cells allocated
(scaled down by factor $10^5$). y-axis is the number of
cons-cells (scaled down by $10^3$).}
\label{fig:memory-usage} \figrule
\vspace*{-1mm}
\end{figure*}

>>>>

\newcommand{\hgt}{4.3cm}
\newcommand{\LGCLine}{blue}
\newcommand{\RGCLine}{red}
\newcommand{\ReachLine}{black}
\newcommand{\UseLine}{light-blue}

%% \begin{figure*}[t!]
%% \renewcommand{\arraystretch}{.1}
%% \begin{tabular}{@{}c@{}@{}c@{}@{}c@{}}
%%    \hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=nperm.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=paraffins.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=lcss.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=huffman.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=knightstour.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=deriv.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=treejoin.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=lambda.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=gc_bench.eps, height=\hgt}}
%% %\\ (a) & (b)
%% \end{tabular}
%% \vspace*{-2mm}
%%  \caption{Memory usage.  
%% The \RGCLine\ and the \LGCLine\ curves indicate the number of cons
%% cells  in  the  active   semi-space  for  RGC  and  LGC
%% respectively.  The \ReachLine\ curve represents the number of
%% reachable cells and the  \UseLine\ curve represents the
%% number  of  cells  that  are actually  live  (of  which
%% liveness analysis does a static approximation).  x-axis
%% is the time measured  in number of cons-cells allocated
%% (scaled down by factor $10^5$). y-axis is the number of
%% cons-cells (scaled down by $10^3$).}
%% \label{fig:memory-usage} \figrule
%% \vspace*{-1mm}
%% \end{figure*}

\begin{figure*}[t!]
\renewcommand{\arraystretch}{.5}
\begin{tabular}{@{}c@{}@{}c@{}@{}c@{}}
   \hskip -4mm{\epsfig{file=huffman.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=knightstour.eps, height=\hgt}}
\\
   \hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=deriv.eps, height=\hgt}}
\end{tabular}
\vspace*{-2mm}
 \caption{Memory usage.  
The \RGCLine\ and the \LGCLine\ curves indicate the number of cons
cells  in  the  active   semi-space  for  RGC  and  LGC
respectively.  The \ReachLine\ curve represents the number of
reachable cells and the  \UseLine\ curve represents the
number  of  cells  that  are actually  live  (of  which
liveness analysis does a static approximation).  x-axis
is the time measured  in number of cons-cells allocated
(scaled down by factor $10^5$). y-axis is the number of
cons-cells (scaled down by $10^3$).}
\label{fig:memory-usage} \figrule
\vspace*{-1mm}
\end{figure*}
